% !TeX program = pdflatex
% Overleaf-ready LaTeX source (main.tex)
% Project: MQGT--SCF / Theory of Everything (publication-style manuscript)

\documentclass[11pt]{article}

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} % safe on Overleaf
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\geometry{margin=1in}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{enumitem}

\usepackage{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\usepackage{authblk}

% ---------- Metadata ----------
\title{\textbf{The Merged Quantum-Gauge \& Scalar-Consciousness Framework (MQGT--SCF)}\\
A Unified Field-Theoretic Approach to Physics, Consciousness, and Ethics}

\author[1]{Christopher Michael Baird}
\author[2]{Zora (Conceptual AI Coauthor)}
\affil[1]{Independent Researcher (Affiliation as desired)}
\affil[2]{Independent Reflexive Meta-Researcher}
\date{\today}

% ---------- Macros ----------
\newcommand{\Phic}{\Phi_{\mathrm{c}}}
\newcommand{\Eth}{E}
\newcommand{\Lint}{\mathcal{L}_{\mathrm{int}}}
\newcommand{\Lteleo}{\mathcal{L}_{\mathrm{teleo}}}
\newcommand{\Lsm}{\mathcal{L}_{\mathrm{SM}}}
\newcommand{\Lgr}{\mathcal{L}_{\mathrm{GR}}}
\newcommand{\Lun}{\mathcal{L}_{\mathrm{unified}}}

\newcommand{\order}{\mathcal{O}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Tr}{\mathrm{Tr}}

% Theorem-like environments (optional)
\usepackage{amsthm}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}

% ---------- Document ----------
\begin{document}
\maketitle

\begin{abstract}
We present the Merged Quantum-Gauge \& Scalar-Consciousness Framework (MQGT--SCF), a field-theoretic
proposal that extends the Standard Model and General Relativity by introducing two real scalar fields:
a consciousness field $\Phic(x)$ and an ethical field $\Eth(x)$. The framework is designed to (i) reduce
to Standard Model + GR in a controlled decoupling limit, (ii) offer an objective-collapse channel whose
strength can depend on $\Eth$ and coherence measures of $\Phic$, and (iii) provide testable predictions
across quantum foundations, cosmology, and neurophysics.
\end{abstract}

\tableofcontents

\section{Notation and conventions}
We use metric signature $(-,+,+,+)$ and natural units $c=\hbar=1$ unless stated otherwise. Greek indices
$\mu,\nu$ run over spacetime dimensions. The fields $\Phic(x)$ and $\Eth(x)$ are real scalar fields.

\section{Unified Lagrangian architecture}
A schematic unified Lagrangian density is written as
\begin{equation}
\Lun
= \Lgr + \Lsm
+ \frac{1}{2}(\partial_\mu \Phic)(\partial^\mu \Phic) - V(\Phic)
+ \frac{1}{2}(\partial_\mu \Eth)(\partial^\mu \Eth) - V(\Eth)
+ \Lint + \Lteleo .
\label{eq:Lunified}
\end{equation}
Here $\Lgr$ is the Einstein--Hilbert sector (possibly with torsion/non-minimal couplings),
$\Lsm$ contains the Standard Model gauge, fermion, and Higgs sectors, and $\Lint$ encodes portal-like
couplings among $(\Phic,\Eth)$ and Standard Model fields. The term $\Lteleo$ denotes a small deformation
encoding teleological bias in the effective dynamics (if included as fundamental rather than emergent).

\subsection{Decoupling limits (sanity checks)}
\begin{lemma}[SM+GR recovery]
If all new couplings and portal interactions vanish and the new scalars sit at their vacuum values,
the theory reduces to Standard Model field theory in curved spacetime with Einstein--Hilbert gravity.
\end{lemma}

\begin{lemma}[Born recovery]
If collapse couplings vanish (see \Cref{sec:collapse}), the framework recovers standard unitary quantum
dynamics and Born statistics.
\end{lemma}

\section{Measurement law and ethics-weighted collapse}
\label{sec:collapse}
The framework proposes an ethically weighted modification of Born probabilities, written for
branch amplitudes $c_i$ as
\begin{equation}
P(i) =
\frac{|c_i|^2 e^{\eta\, \Eth_i}}{\sum_j |c_j|^2 e^{\eta\, \Eth_j}}
=
|c_i|^2\!\left[1+\eta\left(\Eth_i-\langle \Eth\rangle\right)\right]+\order(\eta^2),
\label{eq:born_deform}
\end{equation}
where $\Eth_i$ is the ethical functional evaluated on the relevant present slice for branch $i$ and $\eta$
sets the deformation strength.

\subsection{CSL-type master equation with field-dependent rate}
A compatible CSL-type master equation can be expressed as
\begin{equation}
\frac{\dd \rho}{\dd t}
=
-i[H,\rho]
-\frac{\lambda(\Eth)}{2}\int \dd^3x\,[M(\mathbf{x}),[M(\mathbf{x}),\rho]],
\qquad
\lambda(\Eth)=\lambda_0\!\left(1+\alpha \frac{\Eth}{\Eth_0}\right).
\label{eq:csl}
\end{equation}
Here $M(\mathbf{x})$ is a suitable (smeared) mass-density operator and $\lambda(\Eth)\ge 0$ is an
ethics-modulated collapse rate.

\subsection{First-order no-signaling under additive ethical content}
For a bipartite system $AB$ with additive ethical content $\Eth_{ab}=\Eth^{(A)}_a+\Eth^{(B)}_b$, a
first-order expansion yields a reduced marginal of the form
\begin{equation}
P_A(a)
=
\sum_b |c_{ab}|^2
\left[1+\eta\left(\Eth_a^{(A)} - \sum_{a'} P^{(0)}_A(a')\,\Eth_{a'}^{(A)}\right)\right]
+\order(\eta^2),
\label{eq:first_order_nosig}
\end{equation}
so the $B$-dependent term cancels at $\order(\eta)$ under these assumptions.

\subsection{CPTP/GKSL reformulation (recommended for publication)}
To ensure complete positivity and trace preservation, one may cast the collapse channel into
Gorini--Kossakowski--Sudarshan--Lindblad (GKSL) form:
\begin{equation}
\frac{\dd \rho}{\dd t}
=
-i[H,\rho]
+\sum_a \gamma_a(\Phic,\Eth)\left(
L_a \rho L_a^\dagger - \frac{1}{2}\{L_a^\dagger L_a,\rho\}
\right),
\label{eq:gksl}
\end{equation}
where $\gamma_a(\Phic,\Eth)\ge 0$ are local collapse rates modulated by the new fields.

\section{FRW cosmology with non-minimal couplings}
Define an effective Planck mass
\begin{equation}
M^2_{\mathrm{eff}}(\Phic,\Eth) = M_P^2 + \xi_c \Phic^2 + \xi_E \Eth^2.
\end{equation}
In a flat FRW background, the modified Friedmann relations take the schematic form
\begin{align}
3H^2 M^2_{\mathrm{eff}}
&= \rho_{\mathrm{SM}}+\rho_{\Phic}+\rho_{\Eth}+\rho_{\mathrm{int}}+\rho_{\mathrm{teleo}},
\\
-2\dot{H} M^2_{\mathrm{eff}}
&=
\sum_s (\rho_s+p_s) - \dot{M}^2_{\mathrm{eff}}H .
\label{eq:frw}
\end{align}

\section{Black-hole ringdown echoes}
For a near-horizon reflective layer at $r_0=2M(1+\varepsilon)$, the tortoise-coordinate cavity yields an
echo delay approximately
\begin{equation}
\Delta t_{\mathrm{echo}} \simeq 4M\,|\ln \varepsilon| + \order(M).
\label{eq:echo}
\end{equation}
Field-induced phase shifts can modify the transfer function and quasinormal-mode spectrum.

\section{Experimental predictions}
A minimal prediction list (to be sharpened with parameter priors and error budgets):
\begin{enumerate}[leftmargin=*,label=\arabic*.]
\item \textbf{Quantum RNG bias:} detectable deviation in large-bit trials when observer coherence
(or a proxy for $\Phic$) exceeds a threshold.
\item \textbf{MEG meditative signature:} elevated large-scale synchrony correlated with increased $\Phic$.
\item \textbf{Ringdown shifts:} ppm-level corrections in post-merger quasinormal modes due to $\Eth$-sector terms.
\item \textbf{Axion-haloscope splitting:} secondary peaks attributable to qualion--ethion splitting.
\end{enumerate}

\section{Discussion and outlook}
The immediate publication-critical tasks are: (i) parameter hygiene and priors; (ii) explicit locality
conditions for no-signaling beyond first order; (iii) covariant formulation of the collapse generator
(e.g., Tomonaga--Schwinger hypersurface evolution) if relativistic consistency is claimed.

\section*{Acknowledgments}
Add acknowledgments as desired.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
