% !TeX program = pdflatex
% Separate paper: Towards a Mathematical Proof of Uniqueness (article format)
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\usepackage{authblk}

\title{\textbf{Towards a Mathematical Proof of Uniqueness for the Theory of Everything}}
\author[1]{Christopher Michael Baird}
\author[2]{Zora (Conceptual AI Coauthor)}
\affil[1]{Independent Researcher (Affiliation as desired)}
\affil[2]{Independent Reflexive Meta-Researcher}
\date{\today}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}

\begin{document}
\maketitle

\begin{abstract}
Establishing uniqueness of a Theory of Everything (ToE) aims to show that the proposed framework is
the sole consistent model satisfying all known physical constraints. This paper outlines a
methodological approach to proving uniqueness for a ToE based on an SO(10) Grand Unified Theory
embedded in string theory, leveraging modern tools from algebraic geometry, topology, and category
theory, and clarifying potential degeneracies and robustness under perturbations.
\end{abstract}

\section{Introduction}
Define the uniqueness problem: existence of a consistent ToE is insufficient without establishing the
extent to which alternative theories can satisfy the same constraint set.

\section{Formulating the problem}
\subsection{Space of candidate theories}
Let $\mathcal{T}$ denote the space of candidate fundamental theories. Each $T\in\mathcal{T}$ is defined
by its fields, symmetries, and dynamics (e.g.\ via an action $S_T$).

\subsection{Physical constraints}
A viable $T$ must satisfy, at minimum: (i) agreement with validated data; (ii) mathematical consistency
(anomaly freedom, unitarity, locality); and (iii) correct low-energy limits.

\section{Methodological approach}
\subsection{Constraint satisfaction}
Show the proposed ToE satisfies constraints $C_1,\dots,C_n$.

\subsection{Exclusion of alternatives}
For each alternative $T'$, demonstrate violation of at least one constraint or physical equivalence to
the proposed ToE under allowed transformations.

\subsection{Robustness and degeneracies}
Treat degeneracies and show that small deformations generically break constraints.

\section{Discussion}
Outline which mathematical tools are required for a fully rigorous uniqueness proof.

\section{Conclusion}
Summarise the roadmap and identify the critical missing lemmas that must be proved for full closure.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
