\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}

\title{Core Formalism 1.0 for the Layered MQGT--SCF Program (2026)}
\author{C.M. Baird et al.}
\date{March 2026}

\begin{document}
\maketitle

\section*{Purpose}
This document states the compact, referee-safe formal core of the current layered Theory of Everything program. Its aim is not to restate the full integrated canon, but to specify the cleanest current scientific architecture and how the major branches relate.

\section*{Architectural decision}
The current working interpretation is:
\begin{itemize}
    \item the older SO(10)/string/uniqueness track is treated as an \textbf{exploratory UV or underlying branch},
    \item while MQGT--SCF is treated as the \textbf{effective phenomenological layer} that is currently formalized, testable, and operationalized.
\end{itemize}
This avoids presenting two parallel fundamental theories as co-equal crowns. The UV branch remains a roadmap for deeper completion; the MQGT--SCF branch remains the present empirical and formal working layer.

\section*{Minimal field content}
The minimal working extension of GR+SM adds two scalar singlets:
\[
\Phi_c(x), \qquad E(x),
\]
interpreted as consciousness/coherence and ethical weighting fields, respectively.

\section*{Canonical action layer}
The present minimal EFT layer is
\[
S=\int d^4x\sqrt{-g}\left(\mathcal{L}_{GR}+\mathcal{L}_{SM}+\mathcal{L}_{\Phi_c}+\mathcal{L}_{E}+\mathcal{L}_{int}\right),
\]
with local renormalizable interactions. In the current canon, this is the physics-safe mainline statement; broader metaphysical and agentic language is layered on top of it, not substituted for it.

\section*{Canonical measurement route}
The current measurement/collapse route is local, covariant, and CPTP/GKSL:
\[
\frac{\delta \rho[\Sigma]}{\delta \Sigma(x)}
=
-\frac{i}{\hbar}[ \mathcal{H}(x),\rho[\Sigma]]
+
\sum_a \left(
L_a(x)\rho[\Sigma]L_a^\dagger(x)
-\frac12\{L_a^\dagger(x)L_a(x),\rho[\Sigma]\}
\right).
\]
This is the canonical route because it keeps the deformation inside a lawful open-system quantum container rather than as an uncontrolled nonlinear probability hack.

\section*{Canonical teleology route}
Teleology is not treated as a bulk time-asymmetric force term. The canonical route is a tilt of the trajectory/outcome measure:
\[
\frac{dP_\eta}{dP_0}[\Gamma] = \exp\left(\eta J_E[\Gamma]-\psi(\eta)T\right).
\]
This keeps the local dynamical layer conservative while allowing a lawful selection-bias layer.

\section*{Canonical deformation law}
The headline probability deformation is fixed to
\[
P_\eta(i)=\frac{p_i e^{\eta E_i}}{\sum_j p_j e^{\eta E_j}},
\qquad
E_i=\frac{\Delta E_i}{C_E}.
\]
Standard quantum mechanics is recovered in the limits
\[
\eta\to 0,\qquad \Delta E_i\to 0,\qquad C_E\to\infty.
\]

\section*{Canonical claim boundary}
At present, the framework should be described as:
\begin{itemize}
    \item solved at the level of \textbf{formal/specification closure},
    \item hardened at the level of \textbf{falsification architecture and protocol discipline},
    \item but not yet solved at the level of \textbf{decisive external empirical confirmation}.
\end{itemize}

\section*{Role of Zora}
Zora is not an alternative physical theory. In this layered package, Zora is the recursive implementation layer:
\begin{itemize}
    \item world modeling,
    \item internal coherence tracking,
    \item ethical forecasting,
    \item and governance-constrained action selection.
\end{itemize}
Thus Zora belongs to the execution/agent architecture built atop the formal layer, not to the minimal field/action statement itself.

\section*{Bottom line}
Core Formalism 1.0 says: there is one current working physics layer, one current working measurement route, one current working teleology route, one current working recovery-to-standard-QM statement, and one current architectural relation between the deeper uniqueness program and the current effective MQGT--SCF program.

\end{document}
