\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}

\title{Current Scientific Status of the MQGT--SCF Program (2026)}
\author{C.M. Baird et al.}
\date{March 2026}

\begin{document}
\maketitle

\section*{Abstract}
This memo summarizes the current scientific status of the MQGT--SCF / ToE program as of the present campaign state. The key conclusion is that the framework is substantially advanced at the level of formal specification, falsification architecture, protocol hardening, and reproducibility scaffolding, while empirical closure remains open and is now concentrated into a small number of concrete next experiments and external replication steps.

\section{What is currently solved}
At the formal level, the program now has a canonical spine with the following closure classes fixed or substantially hardened:
\begin{itemize}
    \item one generating action and explicit field dynamics,
    \item one CPTP/GKSL measurement container,
    \item one canonical ethics-weighted Born tilt,
    \item a theorem-oriented operational no-signaling package,
    \item a relativistic Tomonaga--Schwinger container,
    \item teleology as measure tilt rather than as a bulk nonlocal force,
    \item an executable architecture for simulation and protocol testing.
\end{itemize}
In this sense, the framework is solved at the \emph{specification level}, not at the level of decisive external empirical confirmation.

\section{What has been stress-tested}
The staged hypothesis campaign has produced a meaningful internal scientific scaffold:
\begin{itemize}
    \item \textbf{H1:} re-scoped to simulation-primary, with synthetic nulls, shuffled-label nulls, seed robustness, aligned recovery fixtures, and leakage controls.
    \item \textbf{H2:} elevated to the cleanest flagship falsifier, with explicit visibility law and nuisance-budget formalization.
    \item \textbf{H3:} advanced from narrative consistency language to an executable prototype joint posterior/model-comparison package.
\end{itemize}

\section{Current concrete outputs}
\subsection*{H1}
H1 now passes its hardened internal gate structure under the simulation-primary design. This means the current estimator and decision rule survive adversarial nulls and recover a planted aligned effect under the present protocol definition. It does \emph{not} yet mean that a physical branch-selection anomaly has been observed in nature.

\subsection*{H2}
The current recommended physical next step is a Phase-0 benchtop optical visibility pilot. Its purpose is to validate drift accounting, operator discipline, and achieved systematics floor under real instrument conditions. The key quantity is the achieved
\[
\Gamma_{\mathrm{floor}} = \frac{|\ln(1-\delta_{\mathrm{total}})|}{T\Delta x^2},
\]
not a premature discovery claim.

\subsection*{H3}
The current H3 executable package returns a nontrivial jointly weighted region under the implemented H1+H2+fifth-force channel set. This is a genuine internal inference milestone, but it remains bounded to the present implemented channels and should not yet be overstated as final global evidence.

\section{What this means scientifically}
The work no longer looks like a loose speculative bundle. It now supports four stronger scientific claims:
\begin{enumerate}
    \item The framework is materially more coherent than before.
    \item The framework is materially more falsifiable than before.
    \item The framework is materially more reproducible than before.
    \item The remaining uncertainty is increasingly concentrated into specific empirical gates rather than diffuse conceptual ambiguity.
\end{enumerate}

\section{What it does not yet mean}
The current package does \textbf{not} yet justify saying:
\begin{itemize}
    \item that consciousness/ethics/teleology effects have been empirically detected,
    \item that the framework has beaten standard quantum mechanics or GR in live data,
    \item that the full intended channel set has been globally confirmed.
\end{itemize}

\section{Most important remaining scientific bottleneck}
The dominant remaining bottleneck is external empirical closure. The highest-payoff next physical signal is still H2: interferometric visibility suppression beyond the preregistered systematics floor. H1 remains valuable as a hardened stress-test channel, and H3 remains valuable as the cross-channel inference layer, but H2 is the sharpest route to a clean physical blade.

\section{Replication readiness}
The program now has a frozen external contract, artifact manifest, outsider-ready command set, and dedicated replication summary. This means the science is no longer trapped inside private notebooks: an external party can, in principle, attempt to reproduce the current internal chain.

\section{Bottom line}
This is not a dead end. It is also not yet decisive new physics. The honest status is:
\begin{quote}
the program has progressed from visionary synthesis to disciplined candidate science, with formal closure substantially improved and empirical closure now reduced to a finite set of concrete, hostile-testable next steps.
\end{quote}

\end{document}
