% Body-only: for \input into main ToE .tex or paste into Word.
% Ensure empirical_refs.bib and the four PNGs are available to the main project.
% In main .tex: \appendix \input{Empirical_Validation_Appendix_For_ToE}

\section{Empirical Validation: Digitized Constraints and Reproducibility}
\label{sec:empirical_validation}

This appendix summarizes the constraint-translation and reproducibility package for MQGT-SCF: digitized bounds from Lee (2020) Fig.~5 (Yukawa envelope) and Chen \emph{et al.} (2016) E\"{o}t-Wash PRL torsion-balance data. We derive parameter bounds on fifth-force couplings, mixing angles, and Compton wavelengths. All derived MQGT-SCF bounds lie inside the experimentally allowed volume. A full replication ladder and falsification criteria are documented in the repository \texttt{docs/REPLICATION\_LADDER.md} and \texttt{docs/FALSIFICATION\_PACKET.md}.

\subsection{Parameter bounds from Lee (2020)}
Table~\ref{tab:lee_bounds_app} gives the derived envelope from digitized Lee (2020) Fig.~5.

\begin{table}[h]
\caption{Derived MQGT-SCF bounds from digitized Lee (2020) Fig.~5 Yukawa envelope.}
\label{tab:lee_bounds_app}
\begin{tabular}{lcc}
\toprule
Parameter & Minimum & Maximum \\
\midrule
$\lambda_m$ (m)          & $2.07\times10^{-6}$ & $9.45\times10^{-4}$ \\
$m_c$ (eV)               & $2.08\times10^{-4}$ & $0.095$ \\
$\alpha_\text{max}$      & $1.62\times10^{-3}$ & $7.09\times10^{5}$ \\
$\theta_\text{max}$ (rad) & $9.58\times10^{-18}$ & $2.00\times10^{-13}$ \\
$\kappa/\text{VC}_\text{max}$ (GeV) & $6.09\times10^{-16}$ & $1.27\times10^{-11}$ \\
\bottomrule
\end{tabular}
\end{table}

E\"{o}t-Wash (Chen \emph{et al.} 2016) universal coupling bounds suppress predicted fifth-force channels below current torsion-balance sensitivity (30--8000\,nm). The MQGT frequency atlas (214 lines, 19 portals) is consistent with these constraints; seven portal transitions lie within future CASPEr/ARIADNE windows. Born-rule deformation simulations yield $\Delta p < 1.7\times10^{-12}$ per outcome label, consistent with existing QRNG data.

\subsection{Reproducibility and falsification}
Reproduction: clone the spine repo (toe-empirical-validation or toe-2026-updates), pin the commit (\texttt{git rev-parse HEAD}), run the canonical one-command (\texttt{./run\_all.sh} or \texttt{reproduce\_all.py}), and compare outputs to Zenodo or to the figures in the standalone Empirical Validation paper. Falsification criteria: (1)~QRNG finds no deviation under the same operational E; (2)~fifth-force/Eötvös experiments close the allowed window; (3)~multi-channel joint fit fails. See \cite{Lee2020,Chen2016,MQGT2026,ToE2026v230}.
