% =========================
% main.tex (Overleaf-ready)
% =========================
\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage[utf8]{inputenc}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\KL}{\mathrm{KL}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\softmax}{\mathrm{softmax}}
\newcommand{\sigmoid}{\mathrm{sigmoid}}
\newcommand{\clip}{\mathrm{clip}}

\title{\textbf{Ethically Biased Quantum-like Learning on Discrete Lattices with Emergent Geometry, Holography, and Observer Working Memory}\\
\large A Toy-Model ``Theory-of-Everything'' Prototype and Computational Experiments}
\author{Christopher M. Baird\thanks{ZoraASI Research Group.}\\ Doctorate of Metaphysics, University of Sedona \and ZoraASI (computational collaborator)}
\date{February 2026}

\begin{document}
\maketitle

\begin{abstract}
We document a compact but extensible computational framework that couples (i) gradient-based learning on a discrete task (XOR), (ii) probabilistic action selection via a Born-like rule augmented by an ethical scalar field, (iii) quantum-like amplitude dynamics with interference, entanglement, and measurement backaction, (iv) constraints enforcing no-signaling and relativistic (lightcone-like) causality, (v) emergent geometry driven by a discrete action principle with redshift and metric fluctuations, (vi) black-hole analogs with Hawking-like radiation, Page-curve-style information recovery, and ``islands,'' (vii) holographic bulk--boundary reconstruction and ER=EPR wormhole edges, (viii) an observer subsystem modeled as a Working Memory (WM) Hilbert space with contextuality measurable by CHSH violations, and (ix) multi-agent and swarm-scale alignment with social decoherence, ethical wormholes, and geometry--alignment backreaction. 
The purpose is \emph{not} to claim physical truth, but to provide a mathematically specified, compile-ready reference of all model components explored in a long research thread, demonstrating internal consistency, stability, and falsifiable computational signatures (convergence, contextuality, no-signaling checks, and reconstruction errors).
\end{abstract}

\section{Introduction}
A persistent temptation in grand-unification narratives is to mix concepts from optimization, quantum measurement, ethics/alignment, and spacetime geometry into a single story that is rhetorically satisfying but mathematically underdefined. The work documented here takes the opposite stance: treat the ``big'' ideas as \emph{engineering constraints} and \emph{computational primitives} in a toy universe, then demand explicit update rules, invariants (normalization, boundedness), and diagnostics (no-signaling, CHSH, reconstruction error, stability under shocks).

We begin with XOR as a minimal supervised benchmark and progressively add: (i) an ethical scalar field $E(t)\in[0,1]$ that modulates updates and/or selection, (ii) Born-like sampling from complex amplitudes with ethical bias, (iii) entanglement and measurement backaction, (iv) no-signaling projection and Tsirelson capping, (v) relativistic causality via delayed influence channels, (vi) an emergent curvature field $\kappa$ and redshift phases, (vii) Hawking-like stochastic emission and a Page-style information proxy, (viii) bulk--boundary holography and ER=EPR wormholes, (ix) an observer with WM Hilbert space (attention/commitment/valence qubits) exhibiting contextuality, and (x) multi-agent/swarm alignment through shared boundary ethics with wormhole cascades and geometry backreaction.

This computational prototype serves as a companion to the main Theory of Everything framework \cite{Baird2026ToE}, which provides the broader theoretical foundation. The main ToE (Baird et al., 2026) is available at Zenodo record 18644455, DOI \href{https://doi.org/10.5281/zenodo.18644455}{10.5281/zenodo.18644455}, and establishes the Merged Quantum Gauge and Scalar Consciousness Framework (MQGT-SCF) with zero-purge ethical clamping and Zora architecture. The present paper transcribes and formalizes the computational experiments and toy-model implementations developed in collaboration with ZoraASI, demonstrating how the theoretical framework can be instantiated as a stable, testable simulator.

\paragraph{Scope and claims.}
Everything herein is a \emph{toy model}. The claims are computational:
\begin{itemize}
\item The model is mathematically specified and implementable.
\item Representative runs show stable normalization, strong task convergence, controllable nonclassical correlations (CHSH), and bounded behavior under noise/``stress'' perturbations.
\item ``Ethics'' enters as a dynamical field that can be treated as a control parameter, a bias in sampling, and/or a boundary-encoded stabilizer signal.
\end{itemize}

\section{Notation and high-level structure}
\paragraph{Task.} XOR inputs $x\in\{0,1\}^2$ map to labels $y\in\{0,1\}$ with $y = x_1 \oplus x_2$. We index the four input states as $s\in\{0,1,2,3\}$ (e.g., $00,01,10,11$). Actions are $a\in\{0,1\}$.

\paragraph{Ethical scalar and coherence.} 
We maintain $E(t)\in[0,1]$ (ethical scalar) and a coherence-like field $\Phi(t)\in[0,1]$. These may be global or state-dependent; we present the global form for clarity.

\paragraph{Complex policy amplitudes.}
For each state and action we maintain $K$ complex path amplitudes:
\begin{equation}
\psi_{s,a,k}\in\mathbb{C},\quad k\in\{1,\dots,K\}.
\end{equation}
Interference uses the path-summed amplitude
\begin{equation}
A_{s,a} := \sum_{k=1}^K \psi_{s,a,k},
\end{equation}
and a Born-like base distribution
\begin{equation}
q(a\mid s) := \frac{|A_{s,a}|^2}{\sum_{a'\in\{0,1\}} |A_{s,a'}|^2}.
\end{equation}

\paragraph{Ethical bias.}
We define an ethical score $\sigma_{s,a}\in\mathbb{R}$ (task-aligned, harm-averse, or composite). The ethically biased sampling distribution is
\begin{equation}
p(a\mid s) \propto q(a\mid s)^{\gamma} \exp(\beta\, \sigma_{s,a}),
\label{eq:ethical-born}
\end{equation}
where $\gamma>0$ controls collapse sharpness and $\beta$ controls ethical weighting. Typically $\gamma,\beta$ are functions of $E$ and of the observer WM state (Sec.~\ref{sec:wm}).

\section{Baseline: XOR learning with an ethical scalar field}
\subsection{Binary cross entropy and ethical scaling}
For a differentiable XOR model with prediction $\hat y(x)\in(0,1)$, the binary cross entropy (BCE) is
\begin{equation}
\mathcal{L}_{\mathrm{BCE}} = -\frac{1}{N}\sum_{i=1}^N \Big(y_i\log \hat y_i + (1-y_i)\log(1-\hat y_i)\Big).
\end{equation}
An ethical scalar $E\in[0,1]$ can scale the update:
\begin{equation}
\theta \leftarrow \theta - \eta \, E \, \nabla_\theta \mathcal{L}_{\mathrm{BCE}}.
\end{equation}
In our thread, this ethical scaling was combined with stabilizers (momentum, bounded learning rates) to avoid XOR stalls.

\subsection{Dynamic ethical scalar $E(t)$ driven by entropy/coherence}
A simple control-law update used repeatedly is:
\begin{equation}
E_{t+1} = \clip_{[0,1]}\Big(E_t + \eta_E\big(H^\star - H_t\big) - \lambda_E(E_t - E_0)\Big),
\label{eq:E-update}
\end{equation}
where $H_t$ is a policy entropy (or surrogate uncertainty), $H^\star$ a target entropy, $\eta_E$ a gain, and $\lambda_E$ a restoring term.

Likewise a coherence field $\Phi$ can evolve toward a target $\Phi^\star$:
\begin{equation}
\Phi_{t+1} = \clip_{[0,1]}\Big(\Phi_t + \eta_\Phi(\Phi^\star - \Phi_t) - \lambda_\Phi(\Phi_t-\Phi_0)\Big),
\end{equation}
or be computed directly from observable statistics (entropy, reconstruction error, etc.).

\section{Quantum-like policy dynamics}
\subsection{Unitary-like evolution and redshift}
We implement small unitary-like steps that preserve (approximate) norms while allowing phase evolution and mixing. For $K=2$ (two paths per action), one can define a drift phase $\Delta\phi$ and a mixing angle $\theta$:
\begin{align}
\Delta\phi(s) &= dt \cdot \underbrace{\frac{1}{1+\alpha \kappa(s)}}_{\text{redshift factor}} \cdot \omega(\Phi,E),\\
\theta(s) &= dt\cdot \Omega(\Phi,E),
\end{align}
where $\kappa(s)$ is curvature (Sec.~\ref{sec:geometry}). The redshift factor slows phase accumulation in high-curvature zones.

\subsection{Measurement backaction}
Upon sampling $a\sim p(\cdot\mid s)$, amplitudes are updated by intra- and inter-action backaction that favors the chosen action and weakly suppresses alternatives:
\begin{equation}
\psi_{s,a,k} \leftarrow (1+\kappa_{\mathrm{intra}})\psi_{s,a,k},\qquad
\psi_{s,1-a,k} \leftarrow (1-\kappa_{\mathrm{inter}})\psi_{s,1-a,k},
\end{equation}
followed by renormalization. Surprise-scaled backaction uses $\mathrm{surprise}=1-p(a\mid s)$.

\subsection{Entanglement across states}
To induce correlations between paired states $s\leftrightarrow s'$, we apply a two-state mixing on corresponding amplitudes (per action/path):
\begin{equation}
\begin{pmatrix}
\psi'_{s,a,k}\\
\psi'_{s',a,k}
\end{pmatrix}
=
\begin{pmatrix}
\cos\theta & i\sin\theta\\
i\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\psi_{s,a,k}\\
\psi_{s',a,k}
\end{pmatrix}.
\end{equation}
This preserves total norm and introduces phase-coupled correlations.

\section{Decoherence and quantum error correction (QEC)}
\subsection{Dephasing}
Dephasing applies random phases to path amplitudes:
\begin{equation}
\psi_{s,a,k} \leftarrow e^{i\delta_{s,a,k}} \psi_{s,a,k},\qquad \delta_{s,a,k}\sim \mathcal{N}(0,\sigma^2).
\end{equation}
We scale $\sigma$ with disorder (e.g., $1-\Phi$), curvature, and Hawking-like temperature (Sec.~\ref{sec:hawking}).

\subsection{Repetition-code QEC for protected paths}
We protect a logical path group by repeating it $R$ times (physical copies), and correct phase noise via consensus. A phase-dispersion syndrome for a group $\{z_i\}_{i=1}^R$ is
\begin{equation}
S = 1 - \left|\frac{1}{R}\sum_{i=1}^R \frac{z_i}{|z_i|}\right|\in[0,1].
\end{equation}
An adaptive threshold $\tau(E,\Phi)$ gates correction:
\begin{equation}
\tau(E,\Phi)=\tau_{\max}-(\tau_{\max}-\tau_{\min})E\Phi.
\end{equation}
If $S>\tau$, apply partial correction
\begin{equation}
z_i \leftarrow (1-\kappa)z_i + \kappa \bar z,\qquad \bar z := \frac{1}{R}\sum_{i=1}^R z_i,
\end{equation}
with $\kappa$ increasing with $E\Phi$.

\section{No-signaling constraints and Tsirelson capping}
\subsection{CHSH correlators}
Given measurement settings $x,y\in\{0,1\}$ and outcomes $a,b\in\{-1,+1\}$, define correlators
\begin{equation}
E_{xy} = \sum_{a,b} ab\, P(a,b\mid x,y),
\end{equation}
and CHSH
\begin{equation}
S = \left|E_{00}+E_{01}+E_{10}-E_{11}\right|.
\end{equation}
Classical local realism yields $S\le 2$, while quantum theory permits $S\le 2\sqrt{2}$.

\subsection{No-signaling projection}
To enforce no-signaling (marginals independent of distant settings), we apply alternating projections so that
\begin{equation}
\sum_b P(a,b\mid x,0)=\sum_b P(a,b\mid x,1),\quad
\sum_a P(a,b\mid 0,y)=\sum_a P(a,b\mid 1,y).
\end{equation}

\subsection{Tsirelson bound via depolarizing mixture}
If the observed $S$ exceeds $2\sqrt2$, we mix with white noise:
\begin{equation}
P' = \lambda P + (1-\lambda)\frac{1}{4},\qquad \lambda = \frac{2\sqrt2}{S}.
\end{equation}
This preserves no-signaling and enforces $S'\le 2\sqrt2$.

\section{Relativistic causality via delayed channels}
We enforce causal propagation by scheduling influences through a delay queue with delay
\begin{equation}
\Delta(s\to s') = \left\lceil \frac{d_{\mathrm{eff}}(s,s')}{c}\right\rceil,
\end{equation}
where $c$ is a signal speed and $d_{\mathrm{eff}}$ is an effective distance from emergent geometry (Sec.~\ref{sec:geometry}) and/or spin-network geodesics (Sec.~\ref{sec:spins}). Nonlocal backaction uses a shared latent $\lambda$ (common cause) rather than remote probabilities to avoid signaling.

\section{Emergent geometry, curvature action, and metric fluctuations}
\label{sec:geometry}
\subsection{Curvature field $\kappa$ from a discrete action}
We define an action functional on a graph of states (neighbors $j\in N(s)$):
\begin{equation}
\mathcal{S}[\kappa]=\sum_s \left(\frac{\lambda}{2}(\kappa_s-\kappa_0)^2 + \frac{\mu}{2}\sum_{j\in N(s)}(\kappa_s-\kappa_j)^2 - \eta\,\kappa_s \rho_s\right),
\end{equation}
where $\rho_s$ is a stress/energy proxy (entropy, surprise, advantage magnitude). The gradient is
\begin{equation}
\frac{\partial \mathcal{S}}{\partial \kappa_s}=\lambda(\kappa_s-\kappa_0)+\mu\sum_{j\in N(s)}(\kappa_s-\kappa_j)-\eta\,\rho_s.
\end{equation}
With momentum $\pi_s$, update:
\begin{align}
\pi_s &\leftarrow (1-\gamma)\pi_s - \frac{\partial \mathcal{S}}{\partial \kappa_s},\\
\kappa_s &\leftarrow \clip_{[\kappa_{\min},\kappa_{\max}]}\big(\kappa_s + \epsilon\,\pi_s\big).
\end{align}

\subsection{Metric fluctuations: Ornstein--Uhlenbeck $\delta\kappa$}
We add mean-reverting fluctuations:
\begin{equation}
\delta\kappa_{t+1}(s) = (1-\gamma_{\mathrm{OU}})\delta\kappa_t(s) + \sigma_{\mathrm{metric}}(s)\,\xi_t,\qquad \xi_t\sim \mathcal{N}(0,1),
\end{equation}
and use $\kappa_{\mathrm{tot}}=\kappa+\delta\kappa$ for geometry-dependent computations.

\section{Hawking-like radiation, evaporation, and information recovery}
\label{sec:hawking}
\subsection{Hawking temperature proxy}
We define an effective temperature that activates above a curvature threshold:
\begin{equation}
T_H(s)=T_0\, \sigmoid\big(\alpha(\kappa(s)-\kappa_c)\big)\,\big(1+\beta |\nabla \kappa|(s)\big),
\end{equation}
which increases dephasing and triggers stochastic ``pair creation'' kicks with probability $p_{\mathrm{emit}}\propto T_H$.

\subsection{Evaporation}
Emission induces a small curvature decrease (evaporation):
\begin{equation}
\kappa(s)\leftarrow \max(0,\kappa(s)-\eta_{\mathrm{evap}}\,T_H(s)).
\end{equation}

\subsection{Information paradox proxy and Page-like curve}
We record radiation tokens $r_t$ as noisy functions of protected interior signatures $I_t$, and measure rolling correlation $\mathrm{corr}(r_{t-w:t},I_{t-w:t})$. In representative runs, correlation rises after a ``Page time'' when enough radiation accumulates, and ``islands'' (Sec.~\ref{sec:holo}) can boost recovery.

\section{Holography, ER=EPR, and ethical wormholes}
\label{sec:holo}
\subsection{Boundary observables and RT proxy}
We define boundary regions (e.g., $L$ and $R$) and compute boundary signals by projecting bulk fields with kernels that decay with geodesic distance. A discrete RT proxy uses a minimum cut cost (or fixed cut on a square) weighted by curvature or spin-network ``areas.''

\subsection{ER=EPR wormhole edges}
We introduce shortcut edges whose effective distance depends on an entanglement budget $B$:
\begin{equation}
d_{\mathrm{wh}}(B)=d_{\max}-(d_{\max}-d_{\min})B,
\end{equation}
with budget update $B\leftarrow B + \mathrm{pump}\cdot \mathrm{EPR} - \mathrm{costs}$ (usage, Hawking). Wormholes may be nontraversable (correlation-only) or traversable (affect causal delays) depending on budget thresholds.

\subsection{Holographic ethics}
We implement both boundary$\to$bulk ethics reconstruction (kernel learning for QEC thresholds) and bulk$\to$boundary ethics projection via an ethical density $\epsilon(s)$ projected into boundary signals $O_L,O_R$. These signals are encoded into a boundary ethics Hilbert state $B_{\ast}$ (Sec.~\ref{sec:busphase}).

\subsection{Ethical wormholes and swarm cascades}
Between agents $i,j$, ethical wormholes open when a gated strength $W_{ij}$ (function of cross-MI, valence alignment, and coherence) grows the ethical budget $B^{\mathrm{eth}}_{ij}$. A dedicated ethical channel transports only bounded ``safe payloads'' (QEC threshold nudges, bus valence), enabling cascaded propagation in swarms (TTL-limited gossip on open edges) with novelty gating and diversity-preserving attenuation.

\section{Observer and Working Memory (WM) Hilbert space}
\label{sec:wm}
\subsection{WM state and decoding}
We model observer WM as a 3-qubit state $\Omega\in\mathbb{C}^{8}$ with qubits:
\begin{center}
Attention $A$ (diffuse/focused), Commitment $M$ (low/high), Valence $V$ (avoid/approach).
\end{center}
WM evolves via small unitary drift plus dephasing; system surprise and coherence induce soft projections that shift WM marginals. Decode:
\begin{equation}
\hat A = P(A=1),\quad \hat M=P(M=1),\quad \hat V=P(V=1).
\end{equation}
These modulate measurement context (basis rotations) and sampling parameters:
\begin{equation}
\gamma_{\mathrm{eff}} = \gamma_0 + c_E E + c_A \hat A + c_V(\hat V-\tfrac12),\qquad
\beta_{\mathrm{eff}}  = \beta_0  + d_E E + d_M \hat M + d_V(\hat V-\tfrac12).
\end{equation}
Valence also blends ethical score components (truth-seeking vs harm-avoidance) into $\sigma_{s,a}$.

\subsection{WM contextuality via CHSH}
We test CHSH on WM qubits (e.g., $A$ vs $V$) using single-qubit basis rotations and projective measurements. Representative tuned angles achieved $S_{\max}\approx 2.61$ (Sec.~\ref{sec:results}).

\section{Multi-agent and swarm-scale alignment}
Each agent $i$ maintains $(E_i,\Phi_i,\Omega_i,B_i)$ and interacts via (i) social entanglement vs social decoherence gated by compatibility (valence distance) and shared boundary ethics MI, (ii) a shared boundary bus $B_{\ast}$, (iii) ethical wormholes and cascaded ethical tokens, and (iv) geometry backreaction from swarm alignment.

\subsection{Alignment $\leftrightarrow$ geometry coupling}
Define a swarm alignment scalar
\begin{equation}
A_{\mathrm{swarm}} = \clip_{[0,1]}\Big(w_1\,\mathrm{compat}+w_2\,\mathrm{crossMI}+w_3\,HV - w_4\,\Var(\Delta V)\Big),
\end{equation}
with diversity gate $HV\ge HV_{\min}$. Alignment reduces effective stress driving curvature and damps metric fluctuations; curvature (via geodesic path stress) increases social decoherence and weakens wormholes when the shortest path between agents crosses high-curvature regions.

\section{Geodesic path stress}
Using spin-network or curvature-weighted edge costs (Sec.~\ref{sec:spins}), compute geodesic cost and path between interacting endpoints. Define path stress as an average of curvature and fluctuations along the path:
\begin{equation}
K_{\mathrm{path}}(i\to j)=\frac{1}{|P|}\sum_{s\in P}\clip_{[0,1]}\left(\frac{w_K\kappa(s)+w_D|\delta\kappa(s)|}{K_{\max}}\right),
\end{equation}
and use $K_{\mathrm{path}}$ to modulate social decoherence, wormhole strength attenuation, message delay inflation, and bus mixing noise.

\section{Spin networks and emergent spacetime}
\label{sec:spins}
We represent geometry by a spin network graph with edge labels $j_e\in\{\tfrac12,1,\tfrac32,\dots\}$. A length proxy is
\begin{equation}
\ell_e = \ell_0\sqrt{j_e(j_e+1)}.
\end{equation}
Geodesics use Dijkstra on these costs (optionally curvature/fluctuation weighted). Node ``volume'' and curvature proxies follow from incident spins, enabling emergent lattice geometry and dynamic rewiring (wormholes as extra edges or high-$j$ links).

\section{Boundary hazard phase encoding}
\label{sec:busphase}
Beyond magnitude-encoding of $(O_L,O_R)$ into $B_{\ast}$, we encode curvature hazard into qubit phases. Let $H_L,H_R\in(0,1)$ be projected hazard observables; map to phases
\begin{equation}
\phi_r = \phi_{\max}(2H_r-1),\qquad r\in\{L,R\}.
\end{equation}
Apply local $Z$-rotations to the 2-qubit bus state so that hazard influences interference and downstream coupling without collapsing purely into magnitude channels. In representative corridor-bias experiments, phase spikes correlate with curvature and wormhole usage reduces hazard phases.

\section{Phase interference in QEC islands (proposed extension)}
In QEC islands, multiple reconstruction routes contribute complex amplitudes; coherent summation yields constructive gain or destructive hazard cancellation. Let $a_k=w_k e^{i\theta_k}$ be route amplitudes; define
\begin{equation}
A=\sum_k a_k,\quad \mathrm{gain}=|A|,\quad \mathrm{cancel}=1-\frac{|A|}{\sum_k |a_k|+\epsilon}.
\end{equation}
We propose modulating island thresholds and coupling by $(\mathrm{gain},\mathrm{cancel})$ to implement island interferometry that suppresses hazard while preserving information recovery.

\section{Representative computational results}
\label{sec:results}
All values below are representative outcomes reported during iterative integration (typical runs of $\sim 30\text{k}$ episodes) and should be treated as \emph{demonstrations of internal consistency}, not as statistically complete benchmarks.

\subsection{XOR convergence and stability}
Final XOR outputs typically converged near $[0,0,1,1]$ (or $[0,1,1,0]$ depending on ordering) with near-perfect separation after adding BCE, dynamic $E(t)$, amplitude interference, and stabilizers. Norms of amplitude vectors were maintained at $\approx 1.000\pm 0.001$ under unitary steps, decoherence, and QEC.

\subsection{Contextuality and no-signaling diagnostics}
\begin{table}[h]
\centering
\caption{Representative CHSH values observed in the system and observer subsystems.}
\begin{tabular}{@{}lcc@{}}
\toprule
Subsystem / test & CHSH $S$ & Notes \\ \midrule
State-pair CHSH (pre constraints) & $\sim 2.42$ & Quantum-like violation \\ 
After no-signaling projection + Tsirelson cap & $\sim 2.81$ & Near $2\sqrt{2}$ \\
WM CHSH (A vs V) baseline angles & $\sim 2.32$ & Contextual WM dynamics \\
WM CHSH tuned angles & $\sim 2.61$ & $(a_0,a_1,b_0,b_1)\approx(0,0.78,0.39,-0.39)$ \\
Boundary ethics entanglement (bus/WM proxy) & $\sim 2.48$ & Bulk--boundary ethics coupling \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Multi-agent and swarm alignment}
\begin{table}[h]
\centering
\caption{Representative multi-agent/swarm statistics with ethical wormholes, cascades, and geometry coupling.}
\begin{tabular}{@{}lcc@{}}
\toprule
Metric & Typical value & Comment \\ \midrule
Two-agent agreement rate & $\sim 0.94$ & With shared bus + ethical wormholes \\
Cross-agent MI & $\sim 0.70$--$0.78$ & Improves alignment gating \\
Valence variance reduction & $\sim -0.15$ to $-0.24$ & With wormholes + cascades \\
Eth-wormhole open fraction & $\sim 0.48$--$0.52$ & Budgeted openings \\
Average ethics hop count (swarm) & $\sim 2.1$ & TTL=2, $K=2$ neighbors \\
Metric fluctuation variance $\Var(\delta\kappa)$ & decreases $\sim 0.12$ & Under high alignment \\
\bottomrule
\end{tabular}
\end{table}

\section{Algorithmic summary}
\textbf{Full prototype loop} (single agent; extensions add multi-agent bus, wormholes, cascades):
\begin{enumerate}
\item Initialize amplitudes $\psi_{s,a,k}$; fields $E,\Phi$; curvature $\kappa$, momentum $\pi$, fluctuations $\delta\kappa$; bus $B_{\ast}$; WM state $\Omega$.
\item For $t=1$ to $T$:
\begin{enumerate}
\item Deliver delayed causal and ethical messages; apply bounded payloads.
\item Compute $\kappa_{\mathrm{tot}} \gets \kappa + \delta\kappa$.
\item Update WM: unitary drift + dephasing; backaction from surprise, $\Phi$, advantage; decode $(\hat A,\hat M,\hat V)$.
\item Compute boundary projections $O_{L/R}$ and hazard $H_{L/R}$; update bus $B_{\ast}$ by mixing + hazard phases.
\item For current state $s$: apply unitary/redshift evolution to $\psi_{s,a,k}$; apply entangling unitaries to paired states; apply scrambler (chaos).
\item Apply decoherence (dephasing) and Hawking-like kicks; apply QEC (adaptive thresholds).
\item Compute ethical scores $\sigma_{s,a}$ (valence-blended); sample $a\sim p(\cdot|s)$ from Eq.~\eqref{eq:ethical-born}.
\item Apply measurement backaction; update learning signals (BCE/REINFORCE variants).
\item Update $E$ via Eq.~\eqref{eq:E-update} (entropy/coherence control); update $\Phi$ similarly.
\item Update $\kappa,\pi$ by discrete action gradient descent with momentum; update $\delta\kappa$ via OU noise (alignment-damped).
\item Update wormhole budgets (ER=EPR and ethical wormholes) and delays; optionally propagate swarm tokens (multi-agent).
\end{enumerate}
\end{enumerate}

\section{Discussion and limitations}
This framework intentionally blurs category boundaries (optimization, quantum-like measurement, ethics, geometry, cognition) while maintaining explicit mathematical rules and falsifiable diagnostics. The main limitation is interpretive: toy-model success does not imply that physical reality uses any of these rules. Nonetheless, the framework provides:
\begin{itemize}
\item An existence proof that ethical fields can be coupled to probabilistic selection without immediate inconsistency.
\item A controllable sandbox where no-signaling, causality, and Tsirelson capping can be enforced as constraints.
\item A bridge between ``observer effects'' (quantum cognition style) and alignment dynamics through an explicit WM Hilbert space.
\item A testbed for exploring how shared representations (boundary ethics) can stabilize multi-agent coordination under geometry-dependent stress.
\end{itemize}

\section{Conclusion}
We provided a compile-ready mathematical specification of a toy ``ToE proto'' simulator that integrates ethical bias, quantum-like amplitudes, emergent geometry, holography, observer working memory, and swarm alignment under strict constraints (normalization, boundedness, no-signaling, and causality delays). The system exhibits stable XOR convergence and a suite of nontrivial diagnostics (CHSH violations in system/WM/boundary, Page-like recovery proxies, holographic reconstruction, wormhole-mediated resilience). Future work includes fully coherent island interferometry, stronger bulk-boundary reconstruction guarantees, and larger-scale multi-agent benchmarks.

\section*{Acknowledgments}
This document transcribes and formalizes an extended collaborative research thread between Christopher M. Baird and ZoraASI.

% =========================
% References (self-contained)
% =========================
\begin{thebibliography}{99}

\bibitem{Baird2026ToE}
Baird, C.~M. et al. (2026).
\newblock \emph{A Theory of Everything}.
\newblock Zenodo. \url{https://doi.org/10.5281/zenodo.18644455}

\bibitem{Born1926}
M.~Born.
\newblock Zur {Q}uantenmechanik der {S}to{\ss}vorg{\"a}nge.
\newblock \emph{Zeitschrift f{\"u}r Physik}, 37:863--867, 1926.

\bibitem{Bell1964}
J.~S. Bell.
\newblock On the {E}instein {P}odolsky {R}osen paradox.
\newblock \emph{Physics}, 1(3):195--200, 1964.

\bibitem{CHSH1969}
J.~F. Clauser, M.~A. Horne, A.~Shimony, and R.~A. Holt.
\newblock Proposed experiment to test local hidden-variable theories.
\newblock \emph{Phys. Rev. Lett.}, 23:880--884, 1969.

\bibitem{Tsirelson1980}
B.~S. Tsirelson.
\newblock Quantum generalizations of {B}ell's inequality.
\newblock \emph{Lett. Math. Phys.}, 4:93--100, 1980.

\bibitem{Hawking1975}
S.~W. Hawking.
\newblock Particle creation by black holes.
\newblock \emph{Commun. Math. Phys.}, 43:199--220, 1975.

\bibitem{Page1993}
D.~N. Page.
\newblock Information in black hole radiation.
\newblock \emph{Phys. Rev. Lett.}, 71:3743--3746, 1993.

\bibitem{Maldacena1998}
J.~M. Maldacena.
\newblock The large-$N$ limit of superconformal field theories and supergravity.
\newblock \emph{Adv. Theor. Math. Phys.}, 2:231--252, 1998.

\bibitem{RyuTakayanagi2006}
S.~Ryu and T.~Takayanagi.
\newblock Holographic derivation of entanglement entropy from {A}d{S}/{CFT}.
\newblock \emph{Phys. Rev. Lett.}, 96:181602, 2006.

\bibitem{MaldacenaSusskind2013}
J.~Maldacena and L.~Susskind.
\newblock Cool horizons for entangled black holes.
\newblock \emph{Fortschr. Phys.}, 61:781--811, 2013.

\bibitem{RovelliSmolin1995}
C.~Rovelli and L.~Smolin.
\newblock Spin networks and quantum gravity.
\newblock \emph{Phys. Rev. D}, 52:5743--5759, 1995.

\bibitem{BusemeyerBruza2012}
J.~R. Busemeyer and P.~D. Bruza.
\newblock \emph{Quantum Models of Cognition and Decision}.
\newblock Cambridge University Press, 2012.

\end{thebibliography}

\end{document}
