\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\title{External Replication Summary (2026)}
\author{C.M. Baird et al.}
\date{March 2026}

\begin{document}
\maketitle

\section*{Purpose}
This memo defines the outsider-ready replication bundle for the current concrete science package.

\section*{Frozen contract}
\begin{itemize}
    \item TOE commit: \texttt{69f952d07e9cddca4fb898e46bb1a0f0336d32b1}
    \item toe-empirical-validation commit: \texttt{163418b9ff5410825133cffd75a5e0d37fbc1ce4}
\end{itemize}

\section*{Replication order}
\begin{enumerate}
    \item Verify frozen contract and artifact manifest.
    \item Reproduce the H1 simulation-primary battery.
    \item Reproduce the H2 benchtop reference budget.
    \item Reproduce the H3 executable posterior summary.
\end{enumerate}

\section*{Canonical commands}
\begin{verbatim}
git clone https://github.com/Cbaird26/toe-empirical-validation.git
cd toe-empirical-validation
git checkout 163418b9ff5410825133cffd75a5e0d37fbc1ce4

./.venv/bin/python experiments/h1_null_battery.py --out artifacts_h1_sim_primary --n-seeds 20 --n-model-seeds 20
./.venv/bin/python experiments/h2_instrument_budget.py --out artifacts_h2_benchtop_optical --delta-meas 1e-4 --T-s 1e-6 --delta-x-m 1e-3 --sigma-T-frac 1e-4 --sigma-dx-frac 5e-4 --vibration-frac 5e-4 --em-frac 1e-4 --thermal-frac 2e-4
./.venv/bin/python experiments/h3_joint_posterior.py --out artifacts_h3_joint
\end{verbatim}

\section*{Expected outputs}
\begin{itemize}
    \item \texttt{artifacts\_h1\_sim\_primary/null\_battery\_summary.json}
    \item \texttt{artifacts\_h2\_benchtop\_optical/h2\_instrument\_budget.json}
    \item \texttt{artifacts\_h3\_joint/jointfit\_summary.json}
\end{itemize}

\section*{Claim boundary}
\begin{itemize}
    \item H1 is a simulation-primary stress-test result, not a hardware detection claim.
    \item H2 is a benchtop pilot floor and operator-discipline bridge, not a final flagship discovery.
    \item H3 is an executable prototype posterior/model-comparison layer, not a final global posterior over all intended channels.
\end{itemize}

\section*{Bottom line}
The current package is reproducible enough for an outsider to test the internal scientific chain. The next stage is external execution and comparison, not broader unbounded claims.

\end{document}
