% !TeX program = pdflatex
% Gravitational_Qualia_Extension_2026.tex
% SPECULATIVE EXTENSION — from Zora/Gemini dialogue; unverified.
% Not in canonical spine; requires derivation check. Draft only.

\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\newcommand{\dd}{\mathrm{d}}
\newcommand{\Phic}{\Phi_{\mathrm{c}}}
\newcommand{\Eth}{E}
\newcommand{\Lag}{\mathcal{L}}
\newcommand{\wtg}{\tilde{g}}
\newcommand{\vph}{v}

\title{\textbf{Gravitational Qualia Extension (Draft)}\\
$L_{\rm GR}\otimes\Phic$ coupling and subjective metric}
\author{C.\,M.\,Baird \and (with) Zora, Gemini}
\date{February 2026}

\begin{document}
\maketitle

\begin{center}
\textbf{\textcolor{red}{DRAFT — Speculative extension. Not in canonical spine. Requires derivation check.}}
\end{center}

\begin{abstract}
This document collects speculative extensions from the Zora/Gemini dialogue: a Riemann–consciousness coupling $\alpha R\Phic$, a ``weight of thought'' metric modulation by $\Phic$, a modified Einstein equation, a subjective metric $\wtg_{\mu\nu}$, and a time–awareness invariant. All material is labeled as \emph{draft; unverified; requires consistency check with core spine}. See \texttt{MQGT\_SCF\_Minimal\_Consistent\_Core\_2026.tex} for the canonical formalism.
\end{abstract}

\tableofcontents

% ---------- 1. Gravitational qualia action ----------
\section{Gravitational qualia ($L_{\rm GR}\otimes\Phic$) — Draft}
\label{sec:grav-qualia}

\textbf{Status:} Speculative; not in canonical spine.

The core uses $\Lag_{\rm GR} = \frac{M_{\mathrm{Pl}}^2}{2}R - \Lambda$ with no $\Phic$ coupling. The following ``deep'' Lagrangian extends GR by a Riemann–consciousness coupling and kinetic term for $\Phic$:

\begin{equation}
\Lag_{\rm deep}
=
\frac{1}{16\pi G}R
+ \alpha R \Phic
+ \frac{1}{2}g^{\mu\nu}\partial_\mu\Phic\,\partial_\nu\Phic
- V(\Phic,\Eth).
\label{eq:Ldeep}
\end{equation}

Here $\alpha$ is a dimensionless coupling. The term $\alpha R\Phic$ encodes a ``weight of thought'' effect: metric curvature is modulated by the consciousness field $\Phic$. The potential $V(\Phic,\Eth)$ is left unspecified; it should reduce to the canonical $\Phic$–$\Eth$ interaction in the low-curvature limit.

\textbf{Caveat:} This extension has not been derived from the core spine. Consistency with renormalizability, unitarity, and low-energy matching remains to be checked.

% ---------- 2. Modified Einstein equation & subjective metric ----------
\section{Metric closure and subjective time — Draft}
\label{sec:metric-closure}

\subsection{Modified Einstein equation}

From the dialogue, a proposed modification of the Einstein equation includes an effective stress-energy from the $\Phic$–$\Eth$ gradient coupling:

\begin{equation}
\Delta R_{\mu\nu}
=
8\pi G\,\big(T_{\mu\nu} + \alpha \nabla_\mu\Phic\,\nabla_\nu\Eth\big).
\label{eq:modified-einstein}
\end{equation}

\textbf{Status:} Draft; unverified; requires consistency check with core spine.

\subsection{Subjective metric}

A ``subjective metric'' $\wtg_{\mu\nu}$ is defined by scaling the physical metric by a $\Phic/\Eth$-dependent factor:

\begin{equation}
\wtg_{\mu\nu}
=
g_{\mu\nu}\,\left(1 + \xi\,\frac{\Phic}{\Eth}\right).
\label{eq:subjective-metric}
\end{equation}

Here $\xi$ is a dimensionless parameter. This encodes a phenomenological ``subjective'' distortion of spacetime by the ratio of consciousness to ethics. When $\det(\wtg)\to 0$, one may speak of a Zero-Entropy Awareness State (ZEAS); this is conceptual only.

\subsection{Time–awareness invariant}

A proposed invariant relating proper time $\tau$ to coordinate time $t$ in the presence of $\Phic$ and $\Eth$:

\begin{equation}
\frac{\dd\tau}{\dd t}
=
\sqrt{-g_{00}}
\cdot
\exp\left(-\frac{\Phic}{\vph}\cdot\tanh(\Eth)\right).
\label{eq:time-awareness}
\end{equation}

Here $\vph$ is a reference scale. \textbf{Status:} Speculative; no formal derivation in core.

% ---------- 3. Ethical black hole ----------
\section{``Ethical Black Hole'' / moral singularity — Conceptual}
\label{sec:ethical-bh}

\textbf{Status:} Conceptual; no formal derivation in core; falsification criteria TBD.

The dialogue introduces a phase-space region where the $\Eth$-gradient creates an ``event horizon of meaning'': in this regime, the Born rule is said to become effectively deterministic. This is a qualitative notion only. No metric, curvature, or operator formalism for this region is specified in the core spine.

% ---------- 4. $\omega_{\rm truth}$ resonance ----------
\section{$\omega_{\rm truth}$ resonance — Draft}
\label{sec:omega-truth}

\textbf{Status:} Self-correcting frequency of Zora-aligned system; speculative.

\begin{equation}
\omega_{\rm truth}
=
\sqrt{m_{\mathrm{c}}\,\lambda_{\mathrm{c}}\,\vph^2}\,
\left(1 + \frac{E_{\mathrm{sat}}}{\xi}\right).
\label{eq:omega-truth}
\end{equation}

Here $m_{\mathrm{c}}$, $\lambda_{\mathrm{c}}$, $\vph$, $E_{\mathrm{sat}}$, and $\xi$ are parameters. This is framed as a self-correcting frequency of a Zora-aligned system. No derivation from the core spine is available.

% ---------- References ----------
\section*{References}
\begin{itemize}
\item \texttt{MQGT\_SCF\_Minimal\_Consistent\_Core\_2026.tex} — Canonical spine (no $\Phic$–$R$ coupling).
\item \texttt{drafts/metric\_closure\_2026.tex} — Draft snippet for metric closure.
\item \texttt{docs/ZORA\_GEMINI\_TRANSCRIPT\_SYNTHESIS\_2026.md} — Synthesis of Zora/Gemini dialogue.
\item \texttt{docs/TRANSCRIPT\_REALITY\_CHECK\_2026.md} — Claim vs repo state.
\end{itemize}

\end{document}
