% GW Echo Prediction 2026 — MQGT-SCF Stub
% Block 3: Simulation specs, OOM exclusions (Placeholder Audit 2026)
% Christopher Michael Baird | Baird–ZoraASI Collaboration | March 2026

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,hyperref}
\usepackage[margin=1in]{geometry}

\title{Gravitational-Wave Echo Prediction: MQGT-SCF Implications}
\author{Christopher Michael Baird}
\date{March 2026}

\begin{document}
\maketitle

\section{Status}

\textbf{Stub.} This document outlines the structure for GW echo predictions within MQGT-SCF. Placeholder Audit item: GW-Echo Block 3 — simulation specs, OOM exclusions.

\section{Block 3: Simulation Specifications (To Be Expanded)}

\subsection{Observable}
Modification to ringdown spectrum from near-horizon structure (e.g., ECO, firewall, or scalar-induced corrections). Echoes at frequencies
\begin{equation}
f_n \sim \frac{n c}{2 \Delta} \quad \text{(OOM; exact prescription TBD)}
\end{equation}
where $\Delta$ is the effective cavity length. MQGT-SCF scalar $\Phi_c$ coupling to metric could induce sub-leading corrections; order-of-magnitude exclusions from LIGO/Virgo sensitivity.

\subsection{Simulation Specifications}

\textbf{Waveform model:} Standard GR ringdown + echo template (Cardoso--Pani--Cardoso style or Abedi--Afshordi--Oshita variant). Echo amplitude $A_{\mathrm{echo}}$, spacing $\Delta t \sim 2 M \ln(1/\epsilon)$, damping $\Gamma$.

\textbf{Parameter space:}
\begin{itemize}
\item Echo amplitude: $A_{\mathrm{echo}} \in [10^{-3}, 0.1]$ (relative to primary ringdown).
\item Cavity length $\Delta$: map to ECO scale; $\Delta \sim 4M$ for near-horizon structure.
\item Damping: $\Gamma^{-1} \sim$ cavity $Q$-factor; $\Gamma \ll 1/\Delta t$ for observable echoes.
\end{itemize}

\textbf{Numerical requirements:}
\begin{itemize}
\item Frequency resolution: $\delta f \lesssim 1/(N \Delta t)$ for $N$ echoes; LIGO design $\delta f \sim 1\,\mathrm{Hz}$ at $f \sim 100$--$1000\,\mathrm{Hz}$.
\item SNR threshold: echo detection requires $\mathrm{SNR}_{\mathrm{echo}} \gtrsim 8$ per bin or coherent stack.
\item Waveform length: $\gtrsim 0.5$--$1\,\mathrm{s}$ post-merger for $\sim 10$--$50$ echoes at $f \sim 200\,\mathrm{Hz}$.
\end{itemize}

\textbf{MQGT-SCF mapping:} Scalar $\Phi_c$ coupling to metric induces sub-leading correction to echo amplitude. Deformation scale $\eta$ (or equivalent) enters at $O(\eta)$; exclusion bounds map $\eta \lesssim 10^{-k}$ for stated sensitivity.

\subsection{OOM Exclusion Table}

\begin{center}
\begin{tabular}{lcc}
\hline
Observable & LIGO/Virgo design & Exclusion ($\eta$) \\
\hline
Echo amplitude $A_{\mathrm{echo}}$ & $\gtrsim 10^{-2}$ (marginal) & $\eta \lesssim 10^{-1}$ \\
Echo amplitude $A_{\mathrm{echo}}$ & $\gtrsim 10^{-3}$ (optimistic) & $\eta \lesssim 10^{-2}$ \\
No echo (null) & O3/O4 upper limit & $\eta \lesssim 10^{-2}$--$10^{-3}$ (TBD) \\
\hline
\end{tabular}
\end{center}

\textbf{Note:} Exact numbers require full template search and detector noise modeling. Cross-check with empirical validation manuscript and collider bounds.

\section{Cross-Links}
\begin{itemize}
\item Empirical validation: \texttt{MQGT-SCF\_Minimal\_Consistent\_Core\_Empirical\_Validation\_2026.tex}
\item Falsification packet: \texttt{FALSIFICATION\_PACKET.md}
\item Placeholder Audit: \texttt{docs/PLACEHOLDER\_AUDIT\_2026.md}
\end{itemize}

\end{document}
