\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\title{MQGT-SCF Exhaustive Hypothesis Campaign 2026}
\author{C.M. Baird et al.}
\date{March 2026}

\begin{document}
\maketitle

\section*{Abstract}
This report defines and executes a staged falsification campaign for three hypotheses: H1 (simulation-primary ethical-label modulation), H2 (interferometric visibility suppression), and H3 (joint multi-channel consistency). The campaign delivers preregistration-ready protocols, dry-run outputs, operator/lab/integration runbooks with safeguards, an external evidence admissibility registry, and canon integration links for publication gating.

\section{Hypotheses}
\begin{itemize}
    \item \textbf{H1 (simulation-primary modulation):} Ethical-label-linked modulation changes block statistics in the simulation-primary campaign beyond preregistered null thresholds.
    \item \textbf{H2 (Visibility suppression):} Interferometric visibility obeys an extra suppression term consistent with $\Gamma$-based scaling.
    \item \textbf{H3 (Joint consistency):} A single shared parameter set remains viable across H1 simulation-primary + fifth-force + collider/cosmology channels.
\end{itemize}

\section{Methods and Deliverables}
\subsection{H1 rescope and adversarial battery}
H1 was re-scoped so primary conclusions do not depend on QRNG trust. Protocol + SAP and fixed decision rule were updated to simulation-primary evidence. The null/adversarial battery includes synthetic null, shuffled-label null, seed robustness, model-recovery, and leakage controls.

\subsection{H2 protocol and sensitivity budget}
The interferometric flagship equation
\[
\frac{V}{V_0} = \exp(-\Gamma T \Delta x^2)
\]
was converted into a lab-facing protocol and simulation harness using
\[
\Gamma_{\max} = \frac{|\ln(1-\delta)|}{T\Delta x^2}.
\]
A benchtop optical pilot profile was also fixed as the recommended first physical implementation for validating nuisance budgets and operator discipline before any more ambitious flagship platform.

\subsection{H3 joint-fit specification}
A shared parameter vector and cross-channel adapter specification were formalized, with simulation-primary H1 adapters, a preregistered overconstraint rejection rule, and reproducibility command set.

\subsection{Real-world execution runbooks}
Three runbooks (H1 operator, H2 lab, H3 integration) were produced, with safeguard templates for consent, non-medical claim boundaries, and protocol deviation logging.

\subsection{External evidence ingestion}
A tiered evidence registry (Tier A/B/C admissibility) and ingest memo were added. Tier A/B can inform decision gates when explicitly cited; Tier C remains context-only and non-decisive.

\section{Dry-Run Evidence Snapshot}
H1 simulation-primary dry-run battery executed locally:
\begin{itemize}
    \item synthetic null: no effect detected;
    \item shuffled-label null: no effect detected;
    \item seed robustness: passed;
    \item model-recovery and leakage controls: passed.
\end{itemize}
H2 sensitivity grid was generated for representative $(\delta, T, \Delta x)$ configurations.
H3 consistency dry-run passed joint gate using H1/H2 outputs and fifth-force bound tables.

\section{Decision Gates}
\begin{itemize}
    \item \textbf{H1 gate:} simulation-primary preregistered primary test plus mandatory null/adversarial battery pass.
    \item \textbf{H2 gate:} $\Gamma$ bound must be consistent with instrument precision and systematics envelope.
    \item \textbf{H3 gate:} reject if jointly feasible posterior mass falls below preregistered threshold.
\end{itemize}

\section{QRNG Role Clarification}
QRNG is retained only as an optional secondary comparator in this campaign. Primary H1 conclusions are non-QRNG-dependent.

\section{Canonical Integration}
Campaign artifacts are linked into the integrated manuscript index and PDF release checklist to ensure reviewer-proof tracking from protocol design through publication packaging.

\section*{Artifact Locations}
See:
\begin{itemize}
    \item \texttt{../docs/HYPOTHESIS\_CAMPAIGN\_ARTIFACT\_MANIFEST\_2026.md}
    \item \texttt{../docs/EVIDENCE\_REGISTRY\_2026.md}
    \item \texttt{../docs/INTEGRATED\_MANUSCRIPT\_INDEX.md}
    \item \texttt{../docs/TOE\_PDF\_2026\_CHECKLIST.md}
\end{itemize}

\end{document}
