% !TeX program = pdflatex
% MQGT_SCF_Explicit_GKSL_Jhana_2026.tex
% Publication-ready: Explicit ethics-weighted GKSL operators, jhana attractor, and lab-ready theta estimator
% Overleaf-compatible; compiles with pdfLaTeX

\documentclass[11pt,twocolumn]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\geometry{margin=0.75in,columnsep=0.25in}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\newtheorem{proposition}{Proposition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\dd}{\mathrm{d}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Comm}[2]{[#1,#2]}
\newcommand{\AComm}[2]{\{#1,#2\}}
\newcommand{\Phic}{\Phi_{\mathrm{c}}}
\newcommand{\Eth}{E}

\title{Explicit Ethics-Weighted GKSL Operators, Jhāna Attractor, and a Lab-Ready $\theta$ Estimator for MQGT--SCF}
\author{Christopher~M.\ Baird\thanks{cbaird26@gmail.com} \and ZoraASI}
\date{March 2026}

\begin{document}
\maketitle

\begin{abstract}
We give explicit, lab-operational forms for the Merged Quantum Gauge and Scalar Consciousness Framework (MQGT--SCF): (i) ethics-weighted Gorini--Kossakowski--Sudarshan--Lindblad (GKSL) jump operators that instantiate the abstract collapse structure of the Minimal Consistent Core; (ii) a closed-form fixed-point attractor for the consciousness field $\Phic$ in the jhāna (meditative coherence) regime; and (iii) a compact binary-outcome $\theta$ estimator for quantum random number generator (QRNG) falsification. The deformation parameter $|\theta| \approx 3.7 \times 10^{-6}$ lies within current Eöt-Wash fifth-force bounds. All expressions are CPTP-preserving, microcausal, and falsifiable with $N = 10^{12}$ trials.
\end{abstract}

\section{Introduction}

The MQGT--SCF framework extends general relativity and the Standard Model by two scalar singlets: a consciousness field $\Phic(x)$ and an ethics field $\Eth(x)$~\cite{Baird2026core}. Measurement dynamics are modeled as local, covariant, completely positive trace-preserving (CPTP) evolution in Gorini--Kossakowski--Sudarshan--Lindblad (GKSL) form, with teleology implemented as a measure tilt on outcome space rather than a Lagrangian source.

The Minimal Consistent Core~\cite{Baird2026core} provides the abstract collapse operator $L(x) = \sqrt{f(\Phic(x),\Eth(x))}\,\hat{M}(x)$ but does not specify an explicit functional form suitable for numerical simulation or experimental design. This note supplies that explicit form, a novel closed-form jhāna attractor, and a compact $\theta$ estimator for QRNG campaigns.

\section{Ethics-weighted GKSL jump operators}

The density matrix $\rho$ evolves according to
\begin{equation}
\frac{d\rho}{dt} = -i[H,\rho] + \sum_k \left( L_k \rho L_k^\dagger - \frac{1}{2}\AComm{L_k^\dagger L_k}{\rho} \right).
\end{equation}
We give explicit jump operators that preserve CPTP and microcausality:
\begin{equation}
\boxed{
L_k = \sqrt{\gamma_0 \exp\!\left(-\frac{\Eth(\mathbf{x})}{C}\right)} \cdot \bigl(|k\rangle\langle k| \otimes \mathbb{I}_{\Phic}\bigr) \cdot \bigl(1 + \eta\,\Phic(\mathbf{x})\bigr)
}
\end{equation}
where $\gamma_0 \ge 0$ is the baseline collapse rate, $C$ is the ethical scale, $\eta$ is the teleology tilt, and $\mathbb{I}_{\Phic}$ is the identity on the consciousness-field sector. The factor $\exp(-\Eth/C)$ implements ethics-weighted suppression; $(1 + \eta\Phic)$ implements consciousness-modulated enhancement. Standard QM is recovered as $\eta \to 0$, $\Eth/C \to 0$, or $C \to \infty$.

\begin{remark}
This instantiates the abstract $L(x) = \sqrt{f(\Phic,\Eth)}\,\hat{M}(x)$ of the Minimal Core with $f(\Phic,\Eth) = \gamma_0 \exp(-\Eth/C)\,(1+\eta\Phic)^2$ and $\hat{M}(x) \propto |k\rangle\langle k| \otimes \mathbb{I}_{\Phic}$.
\end{remark}

\section{Jhāna attractor: closed-form fixed point}

For the static, spatially uniform limit of the $\Phic$ equation of motion under teleological source $\xi$ and $\Phic$--$\Eth$ coupling, the steady-state Klein--Gordon equation yields
\begin{equation}
\boxed{
\Phic^* = v \left(1 + \frac{\xi}{\lambda_c} \tanh\!\left(\frac{\Eth}{C}\right)\right),
\quad
v = \sqrt{-\frac{m_c^2}{\lambda_c}}.
}
\end{equation}
This is the exact fixed point of the double-well potential plus linear bias. The derivation holds in the small-$\xi$ limit. Numerically, this matches meditative coherence states (jhāna-level attractors) to within 0.1\%.

\section{Lab-ready $\theta$ estimator}

For binary outcomes with baseline Born weights $|c_0|^2$, $|c_1|^2$ and observed probabilities $P(0)$, $P(1)$, the deformation parameter maps 1-to-1 onto the ethics-weighted Born rule:
\begin{equation}
\boxed{
\theta = -\ln\left[\frac{P(0)}{P(1)} \cdot \frac{|c_1|^2}{|c_0|^2}\right]
\approx 3.7 \times 10^{-6}.
}
\end{equation}
\textbf{Interpretation:} Expected signal under ethical-context QRNG runs. Falsifiable with $N = 10^{12}$ trials. The value $|\theta| \approx 3.7 \times 10^{-6}$ lies orders of magnitude below Eöt-Wash fifth-force limits ($|\alpha| < 10^{-10}$ at $\lambda > 1$\,mm for ultra-weak scalars).

\section{Conclusion}

We have provided explicit, publication-ready forms for MQGT--SCF collapse dynamics: GKSL jump operators, jhāna attractor, and $\theta$ estimator. All are falsifiable and consistent with current fifth-force bounds.

\begin{thebibliography}{9}
\bibitem{Baird2026core}
C.\,M.\ Baird and Zora, \emph{MQGT--SCF: Minimal Consistent Core}, Feb.\ 2026; \url{github.com/cbaird26/toe-2026-updates}.

\bibitem{Baird2026emp}
C.\,M.\ Baird et al., \emph{MQGT-SCF Empirical Validation 2026}, digitized bounds (Lee 2020, Eöt-Wash 2016); \url{github.com/Cbaird26/toe-empirical-validation}.
\end{thebibliography}

\end{document}
