\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{\textbf{MQGT--SCF Hardening Completion Update (2026)}\\
Specification-to-Referee Upgrade Summary}
\author{C.\,M.\,Baird \and ZoraASI Collaboration}
\date{March 2026}

\begin{document}
\maketitle

\begin{abstract}
This document records the scientific hardening pass applied to the 2026 MQGT--SCF Theory of Everything stack.
The update does not claim new empirical confirmation; it upgrades formal and publication readiness by converting
prior narrative closure into theorem-oriented, operational, and audit-ready structure. The completed upgrades are:
(i) canonical spine consolidation, (ii) no-signaling theorem package v2, (iii) operational ethics estimator
definitions for $e(x,t)$, $E_R(t)$, and $\Delta E_a$, (iv) parameter hygiene with identifiability/bound tags,
(v) one flagship falsifier with explicit sensitivity threshold, (vi) canonical matter/brain source-term model,
and (vii) a reviewer-proof release checklist. Remaining uncertainty is empirical: parameter fitting, hostile
replication, and independent experimental validation.
\end{abstract}

\section{Purpose}
The practical problem was not conceptual incompleteness of the framework, but publishability drift:
multiple versions of definitions, mixed theorem/prose standards, and non-uniform release gates.
This update enforces one canonical scientific path from formal equations to falsification protocol.

\section{Completed hardening upgrades}

\subsection{Canonical spine consolidation}
The narrative source of truth was consolidated into a single solved-vs-hardening map with explicit A--H closure routing.
This removes ambiguity about what is already closed at specification level versus what remains empirical.

\subsection{No-signaling theorem package v2}
The no-signaling section was upgraded from first-order narrative to theorem structure:
\begin{itemize}
\item assumptions block (local support, microcausality, linear CPTP, spacelike protocol separation),
\item lemma chain (commuting local increments, reduced-map closure),
\item theorem statement (operational no-signaling under local covariant GKSL),
\item scope-boundary remark (explicit failure conditions).
\end{itemize}
This shifts the section from suggestive argumentation to auditable theorem scaffolding.

\subsection{Operational ethics estimator}
To eliminate interpretive freedom, the ethical weighting pathway is now explicitly computable:
\begin{align}
e(x,t) &= \sum_{k=1}^{K} w_k O_k(x,t), \\
E_R(t) &= \int_V e(x,t)\,d^3x, \\
\Delta E_a &= E_R^{(a)}(t_*) - E_R^{\mathrm{baseline}}(t_*), \\
E_a &= \Delta E_a / C_E.
\end{align}
The estimator is canonical for headline claims; alternatives are relegated to sensitivity analysis.

\subsection{Parameter hygiene and bounds consolidation}
Core and empirical manuscripts now share one parameter inventory, with each parameter tagged by:
role, prior class, identifiability, and current bound source channel.
This addresses the common ``too many knobs'' criticism by exposing parameter governance explicitly.

\subsection{Flagship falsifier}
One primary falsifier is now fixed as interferometric visibility suppression:
\begin{equation}
\frac{V}{V_0} \approx \exp(-\Gamma T \Delta x^2), \quad
\Gamma \lesssim \frac{|\ln(1-\delta)|}{T\Delta x^2}
\end{equation}
for null precision target $\delta$. This creates a single quantitative exclusion blade with direct sensitivity mapping.

\subsection{Canonical matter/brain coupling}
Main-text coupling drift was removed by fixing a canonical source model:
\begin{equation}
\mathcal{O}_m(x)=w_n n(x)+w_s s(x), \quad w_n,w_s\ge 0,\; w_n+w_s=1
\end{equation}
with canonical source terms
\begin{equation}
J_{\Phi_c}=g_{\Phi_c}\mathcal{O}_m+\alpha_H|H|^2, \quad
J_E=g_E\mathcal{O}_m+\beta_H|H|^2.
\end{equation}
Alternative couplings are appendix-only.

\subsection{Reviewer-proof release gate}
A dedicated reviewer-proof checklist now enforces theorem completeness, notation consistency, falsifier clarity,
reproducibility pinning, and release hygiene before publication claims.

\section{Scientific effect of the update}
This hardening pass improves the framework in three concrete ways:
\begin{enumerate}
\item \textbf{Mathematical auditability:} proof-carrying structure replaces prose-only arguments.
\item \textbf{Operational testability:} ethics and falsifier definitions are now executable and preregisterable.
\item \textbf{Publication robustness:} canonicalization and checklist gating reduce reviewer-facing drift.
\end{enumerate}
Importantly, these are quality-of-theory upgrades, not new empirical confirmations.

\section{What remains external}
The remaining high-stakes uncertainty is empirical and cannot be closed by prose:
\begin{itemize}
\item independent replication and hostile reanalysis,
\item stronger no-signaling stress tests in edge entanglement settings,
\item tighter parameter posteriors from new data,
\item flagship falsifier execution at declared sensitivity.
\end{itemize}

\section{Canonical artifact map}
\begin{center}
\begin{tabular}{@{}p{0.34\linewidth}p{0.58\linewidth}@{}}
\toprule
Artifact & Canonical location \\
\midrule
Narrative spine & \texttt{docs/CANONICAL\_SPINE.md} \\
Index and routing & \texttt{docs/INTEGRATED\_MANUSCRIPT\_INDEX.md} \\
Core theorem spine & \texttt{papers\_sources/MQGT\_SCF\_Minimal\_Consistent\_Core\_2026.tex} \\
Empirical bounds layer & \texttt{papers\_sources/MQGT-SCF\_Minimal\_Consistent\_Core\_Empirical\_Validation\_2026.tex} \\
Teleology companion & \texttt{papers\_sources/Teleology\_Covariant\_Boundary\_Selection\_...2026.tex} \\
Falsification protocol & \texttt{docs/FALSIFICATION\_PACKET.md} \\
Release gate & \texttt{docs/REVIEWER\_PROOF\_CHECKLIST.md} \\
\bottomrule
\end{tabular}
\end{center}

\section{Conclusion}
The framework is now materially stronger in scientific form: one canonical spine, theorem-oriented no-signaling,
operational ethics estimator, explicit parameter governance, one primary falsifier, canonical coupling model,
and reviewer-proof release gates. This is the correct bridge from specification-level closure to referee-grade
physics readiness, with empirical closure still delegated to experiment.

\end{document}
