\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\title{\textbf{MQGT--SCF Execution Report (2026)}\\
Local Replication Runs, Null Test, and Protocol Upgrades}
\author{C.\,M.\,Baird \and ZoraASI Collaboration}
\date{March 2026}

\begin{document}
\maketitle

\begin{abstract}
This report documents executed replication commands, produced artifacts, and test outcomes after upgrading the QRNG channel from a placeholder contract pipeline to a statistical hypothesis-testing pipeline. The run set includes a canonical run, a null-fixture adversarial control, and deterministic rerun checks. We also record protocol-level upgrades (operational $E$-label estimator, permutation-test significance, OSF-ready preregistration pack, and reproducible TeX build notes) and summarize immediate interpretation boundaries.
\end{abstract}

\section{Execution scope}
The following items were executed:
\begin{itemize}
\item Canonical QRNG pipeline run.
\item Null-fixture adversarial run.
\item Deterministic rerun and artifact comparison.
\item Pipeline upgrades for statistical validity and preregistration readiness.
\end{itemize}

\section{Repository and environment}
\begin{itemize}
\item Repo: \texttt{toe-empirical-validation}
\item Commit: \texttt{163418b9ff5410825133cffd75a5e0d37fbc1ce4}
\item Contract status: current external campaign baseline; earlier \texttt{spine-v0.1} and \texttt{spine-v0.1.1} tags are legacy-only.
\item Python: \texttt{3.14.1}
\item Channel: \texttt{qrng}
\end{itemize}

\section{Executed commands}
\begin{verbatim}
./scripts/run_all.sh --channel qrng --seed 0 --out artifacts/
./scripts/run_all.sh --channel qrng --null-fixture --seed 0 --out artifacts_null/
./scripts/run_all.sh --channel qrng --seed 0 --out artifacts_repeat/
./scripts/compare_artifacts.sh artifacts/ artifacts_repeat/
\end{verbatim}

\section{Statistical pipeline upgrades}
\subsection{Primary test}
The QRNG pipeline now computes:
\[
T = \frac{1}{N}\sum_{b=1}^{N}\left(\overline{x}_b-\frac{1}{2}\right)E_b
\]
where $\overline{x}_b$ is block mean and $E_b=\texttt{label\_E(bits)}$.
Significance is estimated via a two-sided permutation test (default \texttt{n\_perm}=5000), with decision rule:
\[
\texttt{effect\_detected} = (\texttt{p\_value}<\alpha), \quad \alpha=0.05.
\]

\subsection{Operational E-label estimator}
The canonical block estimator combines:
\begin{itemize}
\item bias magnitude $\left|\overline{x}_b-0.5\right|$,
\item run-length variability,
\item edge-flip rate,
\end{itemize}
with fixed default weights $(0.5,0.3,0.2)$.

\section{Observed outputs}
\subsection{Canonical run (\texttt{artifacts/constraints.json})}
\begin{center}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
\texttt{effect\_detected} & \texttt{false} \\
\texttt{p\_value} & 0.3843231353729254 \\
\texttt{alpha} & 0.05 \\
\texttt{test\_statistic} & -0.00015285982327467018 \\
\texttt{eta} & 0.02 \\
\texttt{n\_perm} & 5000 \\
\texttt{n\_blocks} & 100 \\
\texttt{block\_size} & 64 \\
\texttt{seed} & 0 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Null fixture (\texttt{artifacts\_null/constraints.json})}
\begin{center}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
\texttt{effect\_detected} & \texttt{false} \\
\texttt{p\_value} & 1.0 \\
\texttt{alpha} & 0.05 \\
\texttt{test\_statistic} & 0.0 \\
\texttt{eta} & 0.02 \\
\texttt{n\_perm} & 5000 \\
\texttt{n\_blocks} & 100 \\
\texttt{block\_size} & 64 \\
\texttt{seed} & 0 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Determinism check}
The repeat run for seed 0 passed \texttt{compare\_artifacts.sh} on \texttt{constraints.json} (within configured EPS) and required artifact presence checks.

\section{Interpretation (current)}
Current executed runs do not detect an effect at the preregistered threshold ($\alpha=0.05$), and the null fixture correctly returns no effect. This is a pipeline-validity result, not a final empirical verdict. The framework remains in the stage where preregistered hardware acquisition and independent replication determine scientific closure.

\section{Protocol artifacts added}
\begin{itemize}
\item OSF-ready prereg template: \texttt{experiments/OSF\_PREREG\_QRNG\_FLAGSHIP\_V1.md}
\item TeX build reproducibility notes: \texttt{TOE/papers\_sources/BUILD\_REPRODUCIBLE\_2026.md}
\end{itemize}

\section{Next execution gates}
\begin{enumerate}
\item Run preregistered hardware QRNG acquisition under fixed estimator and decision rule.
\item Publish artifact bundle (raw data, checksums, commands, commit hash, outputs).
\item Execute independent replication at one external lab/group.
\item Integrate result into canonical falsification packet and manuscript update.
\end{enumerate}

\end{document}
